C/O and Snowline Locations in Protoplanetary Disks: The Effect of Radial Drift and Viscous Accretion

### 2015-07-20 tex/draft/ms.tex
update

We also apply our active disk model to a transition disk, i.e. a protoplanetary disk with an inner cavity significantly depleted of gas. We choose a disk with an inner gap of radius $r_0=4$ AU, consistent with observations of TW Hya \citep{zhang13}, and with the surface density in the gap reduced by a factor of 1000. Figure \ref{fig:cavity} shows the desorption or final distance for a H$_2$O particle of initial size of 1 m, with the simulation stopped at the same timescales as in Figures \ref{fig:timeplots} and \ref{fig:varMd}. Particles that start at an initial distance interior to the gap drift towards the original snowline, while grains located exterior to the gap stop shortly after crossing the edge gap, due to the decrease in gas pressure inside the cavity, thus forming a snowline at $\sim$$3.8$ AU. This is consistent with the observations of \citet{zhang13} for the H$_2$O snowline being pushed outwards in a transition disk compared to a full disk.

>>>>

We also apply our active disk model to a transition disk, i.e. a protoplanetary disk with an inner cavity significantly depleted of gas. We choose a disk with an inner gap of radius $r_0=4$ AU, consistent with observations of TW Hya \citep{zhang13}, and with the gas surface density in the gap reduced by a factor of 1000. Figure \ref{fig:cavity} shows the desorption or final distance for a H$_2$O particle of initial size of 1 m, with the simulation stopped at the same timescales as in Figures \ref{fig:timeplots} and \ref{fig:varMd}. Particles that start at an initial distance interior to the gap drift towards the original snowline, while grains located exterior to the gap stop shortly after crossing the gap edge, due to the decrease in gas pressure inside the cavity, thus forming a snowline at $\sim$$3.8$ AU. This is consistent with the observations of \citet{zhang13}, which show that the H$_2$O snowline is pushed outwards in a transition disk compared to a full disk.
